Navigating to a greener Europe with 24/7 hourly carbon-free electricity procurement

### 2023-10-14 manuscript/sections/discussion.tex
discussion: add final part and complete section

Another important finding of this work that confirms prevailing understanding is that 24/7 CFE matching creates an early market for advanced energy technologies. Citing an episode of the David Roberts' Volts podcast: \enquote{One reason energy nerds are excited about the 24/7 trend is that it's going to pull forward in time a bunch of questions (and investment decisions) that were going to face grids trying to reach 100 percent CFE anyway} \cite{roberts-intro247CFE}. Further research is needed to better understand how 24/7 CFE commitments push advanced energy technologies along their learning curves, and to estimate the potential economic impact on global decarbonisation costs.

% Where we add: Diverse grid locations and years
According to a comparison of the results over the modeled regions and time periods, voluntary clean energy procurement commitmetns appear to have consistent effects on both participating buyers and system-level decarbonisation.
Based on these findings, this work can provide a basis for generalising the implications of clean energy procurement strategies, while taking into account regional differences in electricity demand, renewable resource availability, legacy power plant fleets, degrees of interconnection, and energy policies, among other factors.

@@

% on the impact on back up flexibility needs
From a system-wide benefits perspective, voluntary commitments to 24/7 CFE reduce the need for flexibility in background electricity systems. 
There will be less investment in gas-fired peaker generators, as well as less need for battery storage elsewhere in the system.
This effect has been explored in Xu et al. (2022) and Riepin~\&~Brown (2022) \cite{riepin-zenodo-systemlevel247,xu-247CFE-report}

@@

>>>>

% Where we converge: on advanced technologies
Another important finding of this work that confirms prevailing understanding is that 24/7 CFE matching creates an early market for advanced energy technologies. Citing an episode of the David Roberts' Volts podcast: \enquote{One reason energy nerds are excited about the 24/7 trend is that it's going to pull forward in time a bunch of questions (and investment decisions) that were going to face grids trying to reach 100 percent CFE anyway} \cite{roberts-intro247CFE}. Further research is needed to better understand how 24/7 CFE commitments push advanced energy technologies along their learning curves, and to estimate the potential economic impact on global decarbonisation costs.

% Where we add: Diverse grid locations and years
According to a comparison of the results over the modeled regions and time periods, voluntary clean energy procurement commitments appear to have consistent effects on both participating buyers and system-level decarbonisation.
Based on these findings, this work can provide a basis for generalising the implications of clean energy procurement strategies, while taking into account regional differences in electricity demand, renewable resource availability, legacy power plant fleets, degrees of interconnection, and energy policies, among other factors.

@@

% on the impact on back up flexibility needs
From a system-wide benefits perspective, voluntary commitments to 24/7 CFE reduce the need for flexibility in background electricity systems. 
There will be less investment in gas-fired peaker generators, as well as less need for battery storage elsewhere in the system.
This effect has been explored by Xu et al. (2022) and Riepin~\&~Brown (2022) \cite{riepin-zenodo-systemlevel247,xu-247CFE-report}

@@

% On "emissionality" approach
\textbf{Is 24/7~CFE the right strategy? --} Last but not least, it is worth mentioning an ongoing discussion whether 24/7 CFE is the right strategy for companies to reduce their carbon emissions.
Some proponents of alternative strategies contend that 24/7 CFE, or \enquote{temporal matching}, may not represent the most effective approach to emissions reduction. 
Instead, they suggest that companies, in their pursuit to reduce system-level carbon emissions, should focus on system-wide impact as measured via short-run marginal emissions accounting (\enquote{emissions matching}).
This argument is based on the rationale that optimising procurement and deployment of carbon-free generators and batteries to cover 24/7 consumption will be different from optimising the assets to \enquote{offset emissions} based on the short-run marginal emission estimates of the grid.
Xu~et~al. (2023) bring this discussion from the realm of arguments into quantitative analysis, discovering that \enquote{emissions matching strategies have zero or near-zero long-run impact on system-level \co emissions} \cite{princeton-247CFEvsEmissionality}.

More work---encompassing the collective contributions of the research community, \gls{ngo}s, policy-makers, and corporate energy buyers---is needed to deepen our understanding of the implications, challenges, and opportunities inherent in various clean energy procurement strategies, guiding us all towards net-zero sustainable energy systems.
